%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {The University of British Columbia} % Organization
    {Remote} % Location
    {Mar. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item 
        {
            Developed LearnCoding, an EdTech web application written in Laravel 
            and jQuery, for teaching coding to undergraduate students, with an 
            emphasis on lesson adaptability for teaching students in 
            different domains, as well as in different spoken and programming 
            languages.
        }
        \item
        {
            Modified \& queried ORM models, created migrations.
        }
        \item
        {
            Created RESTful HTTP endpoints and accessed them via AJAX.
        }
        \item
        {
            Operated in an agile environment, with a Kanban board and weekly Scrum-style meetings
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Technician Summer Student} % Job title
    {School District 67} % Organization
    {Penticton, BC, Canada} % Location
    {May. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item 
        {
            Decommissioned old hardware and deployed new hardware, 
            including server racks, VOIP phones, and workstations. 
        }
        \item
        {
            Managed self, as well as district resources, independently, 
            using a Kanban style system.
        }
        \item
        {
            Used SSH, Nmap, and PuTTY to scan VLANs for malfunctioning hardware. 
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
